Meta-analysis

### 2019-07-23 05_MetaAnalysis.Rmd
updated LSD conversion to loop in the two trials instead of the one. Corrected Standard deviation loop

@@

```{r LSD_2_MSE}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/

Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups
DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) - 
   length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates) # degrees of freedom within groups
n.A <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]
n.B <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[2]
LSD <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error[1]

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
#  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
MSE <- PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

```
![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

```{r sampling_variance}
for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates)){
   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates))}
#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
#                   PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])
# Balance equation 
   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Replicates[j] *
                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$grain_yield.t.ha.[j])))

@@

PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == "mung1112/02",]$Y_error.type <- "SamplingVariance"

@@

# Equation to convert standard deviation to Sampling Variance 
   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error/
               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates))^2
   }

PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error <-

@@

Now for the trickier part creating 'Sampling Variance from NAs.
```{r}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == NA)%>%
   select(Trial_ref)%>%
   distinct()
```

>>>>

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          Y_error.type == "lsd (P=0.05)")%>%
   select(Trial_ref)%>%
   distinct()

@@

![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

```{r LSD_2_Sampling Variance}
# Formula and modifications based off information found at https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/

for(Trial2012 in Trials$Trial_ref){

Tcrit <- 1.697  # 0.05 and DFw = 30 # T critical value for which there is significant difference between two groups; This value is the same for both trials "mung1112/01" and "mung1112/02"
DFw <- sum(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) - 
   length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates) # degrees of freedom within groups
# n.A <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[1]
# n.B <- PM_MB_means[PM_MB_means$Trial_ref == "Trial2012,]$Replicates[2]
LSD <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error[1]

@@

#  LSD = (Tcrit) * sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit) = sqrt(MSW * (1/n.A + 1/n.B))
#  (LSD/Tcrit)^2 = MSW * (1/n.A + 1/n.B)
#  (LSD/Tcrit)^2/(1/n.A + 1/n.B) = MSW
#  MSE <- (LSD/Tcrit)^2/(1/n.A + 1/n.B) # This formula was abandon in favor for the formula in Nugugi et. at (2011)
MSE <- PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[1]*(LSD/Tcrit)^2/2 # method for finding variance in Nugugi et.al (2011) DOI: 10.1094/phyto-08-10-0221

for(j in seq_along(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates)){
   if(j == 1){Sv <- vector(length = length(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates))}
#  Sv[j]^2 = MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
#                   PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])
# Balance equation 
   Sv[j] = sqrt(MSE/(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Replicates[j] *
                  as.numeric(PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$grain_yield.t.ha.[j])))

@@

PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == Trial2012,]$Y_error.type <- "SamplingVariance"

}
```

@@

# Equation to convert standard deviation to Sampling Variance 
   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j]/
               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates[j]))^2
   }

@@

Now for the trickier part creating 'Sampling Variance from NAs.
```{r}
Trials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          is.na(Y_error.type))

   distinct()
```
